Tidy data structure to support exploration and modeling of temporal data

### 2019-01-03 main.Rmd
added a couple sentences to future work

The tidy data abstraction lays a pipeline infrastructure for data analysis modules of transformation, visualization and modelling. Each module communicates between each other, requiring tidy input, producing tidy output, chaining a series of operations together to accomplish the analytic tasks.

@@

The **tsibble** package provides an elegant solution to manage and manipulate medium-sized temporal data in memory.

>>>>

The tidy data abstraction lays a pipeline infrastructure for data analysis modules of transformation, visualization and modelling. Each module communicates between each other, requiring tidy input, producing tidy output, chaining a series of operations together to accomplish the analytic tasks. With the pipe operator `%>%`, read from left to right, and omit intermediate values.

@@

The **tsibble** package provides the grammar of temporal data manipulation, regardless of how the data is stored. Currently, it works for managing and manipulating temporal data frames in memory locally. But it is possible to work with remote tables stored in databases, such as SQLite and MySQL, using exactly the same tsibble code. This is the future work.
